---
title: "Exploratory Data Analysis"
author: "STOR 320.01 Group 6"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

# Import Data Below
# read_csv()
```


# Creator: Kyle Aoki

###Q1: Is there a relationship between production countries and return?

```{r}
movies2 = movies %>% filter(return < 5000)

pc1 = movies2 %>% group_by(production_country_1) %>% summarize(mr = mean(return)) %>% rename(prod = production_country_1) %>% na.omit()
pc2 = movies2 %>% group_by(production_country_2) %>% summarize(mr = mean(return)) %>% rename(prod = production_country_2) %>% na.omit()
pc3 = movies2 %>% group_by(production_country_3) %>% summarize(mr = mean(return)) %>% rename(prod = production_country_3) %>% na.omit()

pc12 = merge(pc1, pc2, by="prod")
pc = merge(pc12, pc3, by="prod")

pcs = pc %>% mutate(ret = (mr.x + mr.y + mr)/3) %>% select(prod, ret) %>% arrange(desc(ret))

ggplot(pcs, aes(reorder(prod, ret), ret)) + geom_bar(stat="identity", fill="tomato2") + coord_flip() + 
  ggtitle("Average Return By Country") + xlab("Country") + ylab("Average Return (%)")

# same plot but only considering positive profits
movies2 = movies %>% filter(return < 5000, profit > 0)

pc1 = movies2 %>% group_by(production_country_1) %>% summarize(mr = mean(return)) %>% rename(prod = production_country_1) %>% na.omit()
pc2 = movies2 %>% group_by(production_country_2) %>% summarize(mr = mean(return)) %>% rename(prod = production_country_2) %>% na.omit()
pc3 = movies2 %>% group_by(production_country_3) %>% summarize(mr = mean(return)) %>% rename(prod = production_country_3) %>% na.omit()

pc12 = merge(pc1, pc2, by="prod")
pc = merge(pc12, pc3, by="prod")
pcs = pc %>% mutate(ret = (mr.x + mr.y + mr)/3) %>% select(prod, ret) %>% arrange(desc(ret))

ggplot(pcs, aes(reorder(prod, ret), ret)) + geom_bar(stat="identity", fill="blue") + coord_flip() + 
  ggtitle("Average Return By Country (Only Positive Profit Movies Considered)") + xlab("Country") + ylab("Average Return (%)")

```




###Q2: Does investing more heavily into a movie increase return?

```{r}
movies %>% filter(return < 7500, budget < 150000000) %>% 
  ggplot(aes(budget, return)) + geom_point(alpha=.5) + geom_smooth(method="lm") + theme_minimal() +
  xlab("Budget of Film") + ylab("Return (%)") + ggtitle("Scatterplot of Return Percentage versus Budget") + 
  theme(plot.title = element_text(hjust = .5))

# The trend is: few high budget movies make high returns. Most high return films are low budget.

movies %>% mutate(buds = budget / 1000000) %>% select(buds, return) %>% filter(return < 1000, buds < 400) %>% ggplot(aes(buds, return)) + geom_point() + geom_smooth(method="lm", se=F) + theme_minimal() + xlab("Budget of Film (In Millions of Dollars)") + ylab("Return (%)") + ggtitle("Scatterplot of Return Percentage versus Budget") + theme(plot.title = element_text(hjust = .5))

# Even controling for extremely high budget/high return movies, the negative trend still holds.

movies %>% mutate(bud = budget / 1000000) %>% filter(return > 0) %>% mutate(log_return = log(return)) %>% ggplot(aes(bud, log_return)) + geom_point() + geom_smooth(method="lm", se=F)

# Adding a log transformation to return still does not break the trend

movies %>% mutate(bud = budget / 1000000) %>% mutate(log_bud = log(bud)) %>% filter(return < 10000) %>% ggplot(aes(log_bud, return)) + geom_point() + geom_smooth()

# Adding a log transformation to budget does not break the trend

movies %>% mutate(bud = budget / 1000000) %>% filter(return > 0) %>% mutate(log_bud = log(bud), log_return = log(return)) %>% ggplot(aes(log_bud, log_return)) + geom_point() + geom_smooth(method="lm", se = F)

# Adding a log transformation to budget AND to return does not break the trend either. The relationship between return and budget is negative.
```




# Interpreter: Brian McGrinder

###Q1: What is the average return by genre?

```{r, include= FALSE}
library(tidyr)
library(tidyselect)
library(tidyverse)
library(broom)
library(rlang)
library(ggplot2)
```

```{r} 

genres_in_genre1 = as.vector(unique(movies$genre_1))

genres_in_genre_2 = as.vector(unique(movies$genre_2))

genres_in_genres_3 = as.vector(unique(movies$genre_3))

genre_sets_combined = c(genres_in_genre1, genres_in_genre_2, genres_in_genres_3)

diffrent_genres = unique(genre_sets_combined)

#There are 20 different genres, I chose to exclude any blank spaces within each of the three columns

avg_crime_return = mean(movies$return[which((movies$genre_1=="Crime")|(movies$genre_2=="Crime")|(movies$genre_3=="Crime"))])

avg_adventure_return = mean(movies$return[which((movies$genre_1=="Adventure")|(movies$genre_2=="Adventure")|(movies$genre_3=="Adventure"))])

avg_animation_return = mean(movies$return[which((movies$genre_1=="Animation")|(movies$genre_2=="Animation")|(movies$genre_3=="Animation"))])

avg_comedy_return = mean(movies$return[which((movies$genre_1=="Comedy")|(movies$genre_2=="Comedy")|(movies$genre_3=="Comedy"))])

avg_drama_return = mean(movies$return[which((movies$genre_1=="Drama")|(movies$genre_2=="Drama")|(movies$genre_3=="Drama"))])

avg_action_return = mean(movies$return[which((movies$genre_1=="Action")|(movies$genre_2=="Action")|(movies$genre_3=="Action"))])

avg_western_return = mean(movies$return[which((movies$genre_1=="Western")|(movies$genre_2=="Western")|(movies$genre_3=="Western"))])

avg_sciencefiction_return = mean(movies$return[which((movies$genre_1=="Science Fiction")|(movies$genre_2=="Science Fiction")|(movies$genre_3=="Science Fiction"))])

avg_mystery_return = mean(movies$return[which((movies$genre_1=="Mystery")|(movies$genre_2=="Mystery")|(movies$genre_3=="Mystery"))])

avg_thriller_return = mean(movies$return[which((movies$genre_1=="Thriller")|(movies$genre_2=="Thriller")|(movies$genre_3=="Thriller"))])

avg_romance_return = mean(movies$return[which((movies$genre_1=="Romance")|(movies$genre_2=="Romance")|(movies$genre_3=="Romance"))])

avg_fantasy_return = mean(movies$return[which((movies$genre_1=="Fantasy")|(movies$genre_2=="Fantasy")|(movies$genre_3=="Fantasy"))])

avg_horror_return = mean(movies$return[which((movies$genre_1=="Horror")|(movies$genre_2=="Horror")|(movies$genre_3=="Horror"))])

avg_war_return = mean(movies$return[which((movies$genre_1=="War")|(movies$genre_2=="War")|(movies$genre_3=="War"))])

avg_family_return = mean(movies$return[which((movies$genre_1=="Family")|(movies$genre_2=="Family")|(movies$genre_3=="Family"))])

avg_documentary_return = mean(movies$return[which((movies$genre_1=="Documentary")|(movies$genre_2=="Documentary")|(movies$genre_3=="Documentary"))])

avg_music_return = mean(movies$return[which((movies$genre_1=="Music")|(movies$genre_2=="Music")|(movies$genre_3=="Music"))])

avg_history_return = mean(movies$return[which((movies$genre_1=="History")|(movies$genre_2=="History")|(movies$genre_3=="History"))])

avg_tvmovie_return = mean(movies$return[which((movies$genre_1=="TV Movie")|(movies$genre_2=="TV Movie")|(movies$genre_3=="TV Movie"))])

avg_foreign_return = mean(movies$return[which((movies$genre_1=="Foreign")|(movies$genre_2=="Foreign")|(movies$genre_3=="Foreign"))])

avg_genre_returns1 = data.frame(avg_foreign_return, avg_tvmovie_return, avg_music_return, avg_documentary_return, avg_family_return, avg_war_return, avg_fantasy_return, avg_horror_return, avg_romance_return, avg_thriller_return, avg_mystery_return, avg_sciencefiction_return, avg_action_return, avg_drama_return, avg_comedy_return, avg_animation_return, avg_adventure_return, avg_crime_return)

avg_genre_returns2 = names(avg_genre_returns1)

avg_genre_returns3 = c(avg_foreign_return, avg_tvmovie_return, avg_music_return, avg_documentary_return, avg_family_return, avg_war_return, avg_fantasy_return, avg_horror_return, avg_romance_return, avg_thriller_return, avg_mystery_return, avg_sciencefiction_return, avg_action_return, avg_drama_return, avg_comedy_return, avg_animation_return, avg_adventure_return, avg_crime_return)

final_genre_returns = data.frame(cbind(avg_genre_returns2, avg_genre_returns3))

final_genre_returns$avg_genre_returns3 = as.numeric(as.character(final_genre_returns$avg_genre_returns3))

final_genre_returns_plot = ggplot(final_genre_returns, aes(avg_genre_returns2, avg_genre_returns3)) + geom_bar(stat = 'identity')+coord_flip() +xlab("Genre")+ylab("Average Returns")+ ggtitle("Average Returns per Genre")

final_genre_returns_plot



#It appears that mystery and horror have by far the highest return in comparison to other genres. It is likely if we move forward we would omit TV Movies as the data for their returns seems to be absent. The other movies returns do vary but not to the extent that the aforementioned genres do. 

```


###Q2: Which directors have the highest average return?

```{r} 
average_director_returns = movies %>%
  group_by(Director) %>%
  summarize(ReturnMean= mean(return),count=n())%>%
  select(Director, ReturnMean, count) %>%
  filter(count >= 10) %>%
  arrange(desc(ReturnMean))

#We removed any directors w/o at least 10 movies directed as we wanted to make sure these directors were consistently making this return (essentially removing “one hit wonders”)

avg_director_returns_plot = ggplot(average_director_returns, aes(Director, ReturnMean)) + geom_bar(stat = 'identity')+coord_flip() +xlab("Director")+ylab("Average Returns")+ ggtitle("Average Returns per Directors (w/ more than 10 movies)")

avg_director_returns_plot


#Of these directors Steven Speilberg, John Carpenter, and Sam Raimi are the runaway leaders in terms of average return per movie directed.
```



# Orator 1: Gabe Stocker

###Q1: What are the production companies with the highest average return?

```{r}
prod1 = movies%>%
group_by(production_company_1)%>%
summarize(n = n())%>%
  arrange(desc(n))%>%
  na.omit()%>%
  subset(n >= 15)
  names(prod1)[1] = c("Prod")

prod2 = movies%>%
group_by(production_company_2)%>%
summarize(n = n())%>%
  arrange(desc(n))%>%  na.omit()%>%

  subset(n >= 10)
  names(prod2)[1] = c("Prod")

prod3 = movies%>%
group_by(production_company_3)%>%
  na.omit()%>%
  summarize(n = n())%>%
  arrange(desc(n))%>%
  subset(n >= 2)
  names(prod3)[1] = c("Prod")
  
top_movies = merge(prod1, prod2,by = "Prod", all = T)
all_movies = merge(prod3, top_movies, by = "Prod", all = T)

all_movies[is.na(all_movies)] = 0
all_movies$count = all_movies$n+all_movies$n.x+all_movies$n.y
all = all_movies%>%
  select(Prod, count)%>%
  arrange(desc(count))%>%
  subset(count >= 30)
#Returns top 29 production companies in terms of movies


#subset movies that have a budget over $10,000,000 to remove cheap movies that may have had return outliers
movies1 = subset(movies, budget >= 10000000)
prod_1 = subset(movies1, production_company_1 %in% all$Prod)%>%
  select(return, production_company_1)
names(prod_1)[2]= c("ProductionCompany")

prod_2 = subset(movies1, production_company_2 %in% all$Prod)%>%
  select(return, production_company_2)
names(prod_2)[2]= c("ProductionCompany")

prod_3 = subset(movies1, production_company_3 %in% all$Prod)%>%
  select(return, production_company_3)
names(prod_3)[2]= c("ProductionCompany")

total = rbind(prod_1,prod_2,prod_3)
total_box = ggplot(total, aes(x = ProductionCompany, y = return))+geom_boxplot()+scale_y_continuous(limits=c(-150,500))+xlab("Production Company")+ylab("Return (Profit/Budget)")+ggtitle("Boxplots of Returns From Top Production Companies")+coord_flip()
total_box

tot_mean= total%>%
  group_by(ProductionCompany)%>%
  summarize(mean = mean(return))
  Avg_Prod_Plot = ggplot(tot_mean, aes(x = ProductionCompany, y = mean))+geom_bar(stat = "identity")+ xlab("Production Company")+ylab("Return (Profit/Budget)")+ggtitle("Average Returns From Top Production Companies")+coord_flip()

```


###Q2: Is there a correlation between IMDB vote score and return?

```{r}
vote.movies = subset(movies, vote_count >50)

  ggplot(vote.movies,aes(x = vote_average, y = return))+geom_point()+scale_y_continuous(limits=c(-150,1500))

#149 values above bounds omitted
#Appears that low score limits your returns but high score doesn’t necessarily correlate with higher returns
```

```{r}
vote = cut(vote.movies$vote_average, breaks=seq(from=min(vote.movies$vote_average)+.1, to=max(vote.movies$vote_average)+1, by=1))
mov = cbind(vote.movies, vote)
mov_subset <- mov[ , c("vote")]  
mov.col = mov[complete.cases(mov_subset),]
#remove two outliers with return values over 100000
mov.col%>%
  subset(return < 100000)%>%
  group_by(vote)%>%
  summarize(mean_return = mean(return))%>%
  ggplot(aes(x = vote, y = mean_return))+geom_bar(stat = "identity")

ggplot(vote.movies,aes(x = vote_average, y = return)) + geom_point()
```



# Orator 2: Andy Henze

###Q1: Does popularity have a correlation with return?


```{r, message=FALSE}
movies = read_csv("C:/Users/andy2639/Desktop/tmdb_5000_super_clean.csv")
```

```{r}
pop_ret <- movies %>% 
  select(popularity, return) %>%
  rename(Popularity = popularity, Return = return)

pop_ret_plot <- pop_ret %>% 
  ggplot(aes(x = Return, y = Popularity)) + 
  geom_point() + 
  ylim(c(0,900)) + 
  xlim(c(0,50000)) 

pop_ret_plot2 <- pop_ret %>% 
  ggplot(aes(x = Return, y = Popularity)) + 
  geom_point() + 
  ylim(c(0,300)) + 
  xlim(c(0,15000)) 

pop_ret_plot3 <- pop_ret %>% 
  ggplot(aes(x = Return, y = Popularity)) + 
  geom_point() + 
  ylim(c(0,150)) + 
  xlim(c(0,5000)) 

pop_ret_plot
pop_ret_plot2
pop_ret_plot3
```
```{r}
# There are a total of 4703 observations. 3 movies made more than 50K$ on returns, and 895 made less than 0$ (a net loss). Considering these observations outliers and removing them, there is no apparent correlation. Removing more outliers (Popularity < 300 and Return < 15000), there is still insufficient evidence to support any kind of correlational claim. Even narrowing the observations further (Pop. < 150 and Ret. < 5000), there exists no apparent correlation between a movie's Popularity score and its Return value.  
```


###Q2: Is there a relationship between release date and IMDB vote score?

```{r}
rel_vote <- movies %>% 
  select(release_date, vote_average) 

year <- tibble(Year = substr(rel_vote$release_date, 1, 4))

month <- tibble(Month = substr(rel_vote$release_date, 6, 7))

year_avg <- mutate(year, Vote = rel_vote$vote_average)

month_avg <- mutate(month, Vote = rel_vote$vote_average)
```


```{r}
year_avg_plot <- year_avg %>% 
  ggplot(aes(x = Year, y = Vote)) +
  geom_point() +
  labs(x = "Release Year",
       y = "Average Vote") +
  theme(axis.text.x = element_text(face="bold", angle=90)) +
  scale_x_discrete(breaks=c("1940","1960","1980","2000")) 

year_avg_plot
```

```{r}
year_avg2 <- filter(year_avg, year_avg$Year > 1960)

year_avg_plot2 <- year_avg2 %>% 
  ggplot(aes(x = Year, y = Vote)) +
  geom_point() +
  labs(x = "Release Year",
       y = "Average Vote") +
  theme(axis.text.x = element_text(face="bold", angle=90)) +
  scale_x_discrete(breaks=c("1970","1980","1990","2000","2010")) 

year_avg_plot2

```

```{r}

month_avg2 <- month_avg %>% 
  filter(month < 13) %>%
  filter(Vote > 0)

month_avg_plot <- month_avg2 %>% 
  ggplot(aes(x = Month, y = Vote)) +
  geom_point() +
  labs(x = "Release Month",
       y = "Average Vote") +
  theme(axis.text.x = element_text(face="bold", angle=90)) +
  scale_x_discrete(breaks=c("01","02","03","04","05","06","07","08","09","10","11","12"))

month_avg_plot
```





# Deliverer: Emily Callahan

###Q1: Which actors have the highest average return?

```{r}
lead = movies%>%
group_by(Leading_Actor)%>%
summarize(n= n())%>%
  arrange(desc(n))%>%
  na.omit()%>%
  subset(n >=20)
  names(lead)[1] = c("Actor")
  
support.lead = movies%>%
group_by(Supporting_Lead)%>%
summarize(n= n())%>%
  arrange(desc(n))%>%
  na.omit()%>%
  subset(n >=10)
  names(support.lead)[1] = c("Actor")

support.actor = movies%>%
group_by(Supporting_Actor)%>%
  na.omit()%>%
  summarize(n= n())%>%
  arrange(desc(n))%>%
  subset(n >= 2)
  names(support.actor)[1] = c("Actor")
  
new.lead =lead[-c(1), ]
new.support.lead= support.lead[-c(1), ]
  
top_actors = merge(new.lead, new.support.lead,by = "Actor", all = T)
all_actors = merge(support.actor, top_actors, by = "Actor", all = T)
all_actors[is.na(all_actors)] = 0
all_actors$count = all_actors$n+all_actors$n.x+all_actors$n.y
actors_1 = all_actors%>%
  select(Actor, count)%>%
  arrange(desc(count))%>%
  subset(count >= 5)
#Returns top 31 actors

lead_1 = subset(movies, Leading_Actor %in% actors_1$Actor)%>%
  select(return, Leading_Actor)
names(lead_1)[2]= c("Actor")

supporting_lead_1 = subset(movies, Supporting_Lead %in% actors_1$Actor)%>%
  select(return, Supporting_Lead)
names(supporting_lead_1)[2]= c("Actor")

supporting_actor_1 = subset(movies, Supporting_Actor %in% actors_1$Actor)%>%
  select(return, Supporting_Actor)
names(supporting_actor_1)[2]= c("Actor")

total.actor = rbind(lead_1,supporting_lead_1,supporting_actor_1)
avg_mean= total.actor%>%
  group_by(Actor)%>%
  summarize(avg_return = mean(return)) %>%
  arrange(desc(avg_return)) %>%
  filter(avg_return >= 175)
Avg_Return_Plot = ggplot(avg_mean, aes(x = Actor, y = avg_return))+geom_bar(stat = "identity")+ xlab("Actor")+ylab("Average Return (Profit/Budget)")+ggtitle("Average Returns From Top Actors")+coord_flip()
Avg_Return_Plot

```


###Q2: Does the number of languages offered have a relationship with return?

```{r}
total.lang = movies %>% group_by(total_spoken_languages) %>% summarize(avg_return = mean(return), count = n())

ggplot(total.lang, aes(x=total_spoken_languages, y=avg_return)) + 
  geom_bar(stat='identity', fill="blue") +
  labs(title="Number of Languages v. Return") + xlab("Total Number of Languages") + 
  ylab("Average Return (%)")

#The number of languages offered does not have a relationship with return
```


# Follow-up Questions

### New Questions Based Off Initial Investigation

- Q1: Why is it that only movies with relatively low budgets experience high returns?
- Q2: WRITE QUESTION HERE
- Q3: Why do the genres “Horror” and “Thriller” have significantly higher returns than all the other genres?
- Q4: What is the gender ratio for the top 100 actors in terms of average return?

### Investigation of Follow-up Questions

GIVE WHAT 2 QUESTIONS YOU ATTEMPTED TO INVESTIGATE FURTHER IN COMPLETE SENTENCES (*Example:* Our group decided to investigate Q2 and Q4 in further detail.)

SHOW AT LEAST 2 TABLES OR FIGURES BELOW THAT EXPLORE ANSWERS FOR THE QUESTIONS YOU ARE INVESTIGATING FURTHER.


### Question 1: We decided to investigate question 1 further, which is understanding why only movies with relatively low budgets experience high returns.

```{r}
movies %>% filter(return > 2000, return < 400000) %>% ggplot(aes(release_date, return)) + geom_point() + geom_smooth(method='lm', se=F, color='red') + ggtitle("Release Date versus Return for Films with 2000% + Return") + xlab("Release Date") + ylab("Return (%)")

high_ret = movies %>% filter(return > 2000, return < 35000) %>% arrange(desc(return))

head(high_ret, 25) %>% ggplot(aes(reorder(title, return), return)) + geom_bar(stat='identity', fill="tomato2") + coord_flip() + ggtitle("Top Movies by Return (%)") + ylab("Return (%)") + xlab("Title of Movie")
```

For question 1, what we are trying to understand is why there are films that have ludicrously high returns, and why those films are always lower budget. The answer, as one can see from the plots above, is twofold: (1) the first reason is that the movie in question is a “Classic”, and (2) the second reason is that the movie in question is a low budget film that was as successful as a normal film.

First, there are “classics”, such as Snow White and the Seven Dwarves, which have had by this point almost an entire century to make its production company money. Thus, the returns will be quite high. Movies like Bambi, Gone With the Wind, Jaws, E.T., and Star Wars are all considered “classics” and are still being watched today. Their return is so high because of the length of time they have had to produce value for its production company.

Secondly, there are low budget films, often comedies, which are a major hit, and are thus high return movies because of the large ratio between budget and revenue. Since return is calculated by having the budget in the denominator and revenue in the numerator, a film with both a small denominator and large numerator will yield a high return value. These films can be more modern, having been released recently, but will not generate revenue for its production company for a long length of time like “classic” movies. 


### Question 2: How has IMBD score influenced returns over time?

```{r}
library(readr)
library(dplyr)
library(ggplot2)
tmdb_5000_super_clean <- read_csv("Downloads/tmdb_5000_super_clean.csv")
head(tmdb_5000_super_clean)
```

```{r}
movies = tmdb_5000_super_clean
prod1 = movies%>%
group_by(production_company_1)%>%
summarize(n = n())%>%
  arrange(desc(n))%>%
  na.omit()%>%
  subset(n >= 15)
  names(prod1)[1] = c("Prod")

prod2 = movies%>%
group_by(production_company_2)%>%
summarize(n = n())%>%
  arrange(desc(n))%>%
  na.omit()%>%
  subset(n >= 10)
  names(prod2)[1] = c("Prod")

prod3 = movies%>%
group_by(production_company_3)%>%
  na.omit()%>%
  summarize(n = n())%>%
  arrange(desc(n))%>%
  subset(n >= 2)
  names(prod3)[1] = c("Prod")
  
top_movies = merge(prod1, prod2,by = "Prod", all = T)
all_movies = merge(prod3, top_movies, by = "Prod", all = T)

all_movies[is.na(all_movies)] = 0
all_movies$count = all_movies$n+all_movies$n.x+all_movies$n.y
all = all_movies%>%
  select(Prod, count)%>%
  arrange(desc(count))%>%
  subset(count >= 30)
```
Returns top 29 production companies in terms of movies

```{r}
#subset movies that have a budget over $10,000,000 to remove cheap movies that may have had return outliars
movies1 = subset(movies, budget >= 10000000)
prod_1 = subset(movies1, production_company_1 %in% all$Prod)%>%
  select(return, production_company_1)
names(prod_1)[2]= c("ProductionCompany")

prod_2 = subset(movies1, production_company_2 %in% all$Prod)%>%
  select(return, production_company_2)
names(prod_2)[2]= c("ProductionCompany")

prod_3 = subset(movies1, production_company_3 %in% all$Prod)%>%
  select(return, production_company_3)
names(prod_3)[2]= c("ProductionCompany")

total = rbind(prod_1,prod_2,prod_3)
total_box = ggplot(total, aes(x = ProductionCompany, y = return))+geom_boxplot()+scale_y_continuous(limits=c(-150,500))+xlab("Production Company")+ylab("Return (Profit/Budget)")+ggtitle("Boxplots of Returns From Top Production Companies")+coord_flip()
ggsave("ProductionBox.png")

```
```{r}
tot_mean= total%>%
  group_by(ProductionCompany)%>%
  summarize(mean = mean(return))
  Avg_Prod_Plot = ggplot(tot_mean, aes(x = ProductionCompany, y = mean))+geom_bar(stat = "identity")+ xlab("Production Company")+ylab("Return (Profit/Budget)")+ggtitle("Average Returns From Top Production Companies")+coord_flip()
  ggsave("ProductionAverage.png")
```




```{r}
vote.movies = subset(movies, vote_count >50)

  ggplot(vote.movies,aes(x = vote_average, y = return))+geom_point()+scale_y_continuous(limits=c(-150,1500))
#149 values above bounds omitted
  ggsave("VotePlot.png")

```
```{r}
vote = cut(vote.movies$vote_average, breaks=seq(from=min(vote.movies$vote_average)+.1, to=max(vote.movies$vote_average)+1, by=1))
mov = cbind(vote.movies, vote)
mov_subset <- mov[ , c("vote")]  
mov.col = mov[complete.cases(mov_subset),]
#remove two ouliers with return values over 100000
mov.col%>%
  subset(return < 100000)%>%
  group_by(vote)%>%
  summarize(mean_return = mean(return))%>%
  ggplot(aes(x = vote, y = mean_return))+geom_bar(stat = "identity")
mov.col%>%
  subset(return < 100000)%>%
ggplot(aes(x = vote_average, y = return))+geom_point()
ggsave("VoteBar.png")

```
```{r}
movie.year = separate(mov.col, "release_date", c("Year", "Month", "Day"), sep = "-")
min(movie.year$Year)
max(movie.year$Year)
movie.year$yeargroup = findInterval(movie.year$Year, c(1910, 1920, 1930, 1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))

```

```{r}
movie.years = movie.year%>%
  filter(return < 30000)%>%
  select(return,vote_average,vote_count, vote, Year, yeargroup)%>%
  group_by(yeargroup,vote)%>%
  summarize(year.avg = mean(return), count = n())%>%
  select(vote, yeargroup, year.avg, count)
#Removed all movies with return over 30000 to eliminate outliers

movie.years$yeargroup = as.numeric(movie.years$yeargroup)


year.movie = movie.years%>%
  filter(yeargroup>7)%>%
  filter(vote != "(3,4]")

#Removed all movies before 1980s due to lack of data causing large skew (less than 100 movies per decade). Already had removed movies with less than 50 votes.

  imbd.time = ggplot(data = year.movie, aes(x = (vote), y = (year.avg), fill = factor(yeargroup))) +   
  geom_bar( position = position_dodge(), stat="identity")
ggsave("IMBDOverTime.pdf", imbd.time)
```




```{r}
library(readr)
library(dplyr)
library(ggplot2)
```

```{r}
prod1 = movies%>%
group_by(production_company_1)%>%
summarize(n = n())%>%
  arrange(desc(n))%>%
  na.omit()%>%
  subset(n >= 15)
  names(prod1)[1] = c("Prod")

prod2 = movies%>%
group_by(production_company_2)%>%
summarize(n = n())%>%
  arrange(desc(n))%>%
  na.omit()%>%
  subset(n >= 10)
  names(prod2)[1] = c("Prod")

prod3 = movies%>%
group_by(production_company_3)%>%
  na.omit()%>%
  summarize(n = n())%>%
  arrange(desc(n))%>%
  subset(n >= 2)
  names(prod3)[1] = c("Prod")
  
top_movies = merge(prod1, prod2,by = "Prod", all = T)
all_movies = merge(prod3, top_movies, by = "Prod", all = T)

all_movies[is.na(all_movies)] = 0
all_movies$count = all_movies$n+all_movies$n.x+all_movies$n.y
all = all_movies%>%
  select(Prod, count)%>%
  arrange(desc(count))%>%
  subset(count >= 30)
```
Returns top 29 production companies in terms of movies

```{r}
#subset movies that have a budget over $10,000,000 to remove cheap movies that may have had return outliars
movies1 = subset(movies, budget >= 10000000)
prod_1 = subset(movies1, production_company_1 %in% all$Prod)%>%
  select(return, production_company_1)
names(prod_1)[2]= c("ProductionCompany")

prod_2 = subset(movies1, production_company_2 %in% all$Prod)%>%
  select(return, production_company_2)
names(prod_2)[2]= c("ProductionCompany")

prod_3 = subset(movies1, production_company_3 %in% all$Prod)%>%
  select(return, production_company_3)
names(prod_3)[2]= c("ProductionCompany")

total = rbind(prod_1,prod_2,prod_3)
total_box = ggplot(total, aes(x = ProductionCompany, y = return))+geom_boxplot()+scale_y_continuous(limits=c(-150,500))+xlab("Production Company")+ylab("Return (Profit/Budget)")+ggtitle("Boxplots of Returns From Top Production Companies")+coord_flip()

```

```{r}
tot_mean= total%>%
  group_by(ProductionCompany)%>%
  summarize(mean = mean(return))
  Avg_Prod_Plot = ggplot(tot_mean, aes(x = ProductionCompany, y = mean))+geom_bar(stat = "identity")+ xlab("Production Company")+ylab("Return (Profit/Budget)")+ggtitle("Average Returns From Top Production Companies")+coord_flip()
```


```{r}
vote.movies = subset(movies, vote_count >50)
```

```{r}
vote = cut(vote.movies$vote_average, breaks=seq(from=min(vote.movies$vote_average)+.1, to=max(vote.movies$vote_average)+1, by=1))
mov = cbind(vote.movies, vote)
mov_subset <- mov[ , c("vote")]  
mov.col = mov[complete.cases(mov_subset),]
#remove two ouliers with return values over 100000
```

```{r}
movie.year = separate(mov.col, "release_date", c("Year", "Month", "Day"), sep = "-")
min(movie.year$Year)
max(movie.year$Year)
movie.year$yeargroup = findInterval(movie.year$Year, c(1910, 1920, 1930, 1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))

```

```{r}
movie.years = movie.year%>%
  filter(return < 30000)%>%
  select(return,vote_average,vote_count, vote, Year, yeargroup)%>%
  group_by(yeargroup,vote)%>%
  summarize(year.avg = mean(return), count = n())%>%
  select(vote, yeargroup, year.avg, count)
sum(movie.years$count)
#Removed all movies with return over 30000 to eliminate outliers
#Shows that 3606 movies included in set
movie.years$yeargroup = as.numeric(movie.years$yeargroup)



year.movie = movie.years%>%
  filter(yeargroup>7)%>%
  filter(vote != "(3,4]")

#Removed all movies before 1980s due to lack of data causing large skew (less than 100 movies per decade). Already had removed movies with less than 50 votes.

imbd.time = ggplot(data = year.movie, aes(x = (vote), y = (year.avg), fill = factor(yeargroup))) + geom_bar( position = position_dodge(), stat="identity") + scale_fill_discrete(name = "Year Group", labels = c("Before 1970s", "70-90s", "90-00s", "2010+"))
imbd.time

```


### Question 3: Why do the genres “Horror” and “Mystery” have significantly higher returns than all the other genres?

### Question 4: What is the gender ratio for the top 100 actors in terms of average return?


#Summary

GIVE A 2 PARAGRAPH SUMMARY. 

PARAGRAPH 1 SHOULD DESCRIBE WHAT YOU LEARNED ABOUT YOUR DATA FROM INVESTIGATING THE INITIAL QUESTIONS. DID YOU FIND ANYTHING UNUSUAL IN YOUR DATA? DID ANYTHING SURPRISE YOU? WHICH OF THE INITIAL QUESTIONS WERE HELPFUL IN LEADING YOU TO MORE QUESTIONS?

	After investigating our initial questions, our group found that our Movies data did not have relationships between variables that we were expecting obvious relationships between. The group, having a basic knowledge of movie culture, was anticipating clear and distinct correlations based on each of our assumptions coming into this analysis. For example, as a group, we expected that a higher movie budget would lead to a higher average return based on the common logic “the more you put into it, the more you get out of it.” However, after cleaning the data and creating visualizations, we found this not to be the case as our data showed us that there is a negative relationship between budget and return. Within our data we found a few things to be unusual. Three major things we found to be unusual were that there was no relationship between the average popularity score and the return value, there was not a clear correlation between high IMDB vote scores and high average returns, and there was no relation between the release months and years and the average IMDB vote score. These results in particular surprised us because we thought that popular movies would earn greater returns, that high IMDB vote scores would encourage viewership which would as a result increase return, and that IMDB vote scores would be higher as time has progressed. However, our data surprised us and proved most of our initial expectations false. In creating our follow up questions, the questions “Does investing more heavily into a movie increase return,” “Is there a correlation between IMDB vote score and return,” “What is the average return by genre,” and “which actors have the highest average return” were the most helpful in leading us into deeper analysis. These four initial questions were the most helpful because they helped us explain the strange or surprising results we found in our initial exploration of the data.



PARAGRAPH 2 SHOULD SUMMARIZE WHAT YOU LEARNED FROM INVESTIGATING THE FOLLOW-UP QUESTIONS. WHY ARE THESE FOLLOW-UP QUESTIONS INTERESTING FOR INVESTIGATION? DESCRIBE THE TABLES/FIGURES YOU USED TO EXPLORE ANSWERS TO THESE FOLLOW-UP QUESTIONS? WHAT DID YOU LEARN FROM THE TABLES/FIGURES REGARDING THE FOLLOW-UP QUESTIONS YOU PROPOSED?

The first question we decided to examine further was “Why is it that only movies with relatively low budgets experience high returns?” This was worthy of further investigation as the difference in returns was absolutely ludicrous comparatively to larger budget films. It is important to note that these returns were not in gross revenue, but rather by dividing the revenue of the movie by its budget. To tackle this question, we filtered our results to account for outliers while looking for a high return, limiting the return percentage to between 2000 and 35000 to stratify our results. We also used a scatterplot to see when these films were released as we believed that may have factored into this anomaly. We also filtered the returns of movies shown in this plot, creating a minimum of 2000 percent and maximum at 400000 percent returns. From the investigation, we found that the answer is broken up into two parts. From the scatterplot we noticed a trend of high returns for movies released a significant amount of time ago, some even around a century old. In these cases, these movies are “classics” which allows them to stay relevant despite being released a long time ago, so they continuously accrue revenue over time. Examples of this include Snow White and John Carpenter’s Halloween. The second part to this answer is that there are lower budget films, in most cases comedies, which are major hits, and are thus high return movies because of the large ratio between budget and revenue. These films are more modern, having been released recently, but will not generate revenue for its production company for a long length of time like the aforementioned “classic” movies. Movies like “Napoleon Dynamite” have absurdly high returns because the cost of production was a crappy $150 camera and a couple of microphones. The “actors” also had a low labor cost. The second question we decided to examine further was how IMBD score’s impact upon the returns of movies over time. In order to create a visual, we narrowed the focus of the examination to just the returns of the top 29 production companies and also removed what we felt were two outliers which skewed the results of the graphic (return over 1000000). We then broke down the returns into different categories based on their IMDB score as well as the year in which they were released. To visualize this, we created a bar chart that indicates how movies with different IMDB rating scores have performed in different time periods (2010’s, 1990-2000’s, 1970-1990’s etc.). From this graphic we noticed that over time the returns of movies in general seemed to fall, and the distribution across returns and IMDB scores seems to be more uniform. This indicates that as time has gone on, IMDB score has impacted how many people see the movie less and less. This is possibly due to the fact that the average consumer has become desensitized to these critics over time.